This study's primary purpose was to evaluate the predictive performance of
various machine learning models to real data on Airbnb listings in the city of
New York.  The methods used in this study consisted of simple and multiple
linear regression, ridge regression, lasso regression, and XGBoost. The models
were compared and assessed using mean square error and coefficient of
determination criteria.

The research has shown that gradient boosting with all features (XGBoost) performs
the best among all models. Ridge regression has the second-best performance.
While Lasso's performance is not as good as Ridge Regression and XGBoost, Lasso
performs feature selection. With Lasso, we were able to find a sparse model,
which includes only relevant variables.
Linear Regression performs the worst proved that the abundance of features leads
to high variance and weak performance (overfitting).

The second aim of this study was to identify which characteristics of an Airbnb
listing were most important in predicting the price. We found that the most
critical feature is whether the type of listing is an entire home or not. The
second most important feature is the number of bathrooms. Also, location
features play an essential role in predicting price. These findings help
develop a reliable price prediction model to aid the Airbnb hosts in maximizing
their earnings.

In future work, we would like to:
\begin{enumerate}
  \item Experiment with the data with Neural Network.
  \item Find a way to include listing's photo quality as a predictor.
  \item Incorporate customer reviews feature through sentiment analysis.
\end{enumerate}
